---
title: "Boston_LR_Anshuman"
author: "Anshuman Dash"
date: "June 26, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Load all the libraries
```{r}
library(MASS)
library(sandwich)
library(lmtest)
library(car)

```
#Load the Boston Data file, Boston file is avaliable in MASS library
Explore the Boston Data
```{r}
Bostondf= Boston

#Explore Boston Data
head(Bostondf)
str(Bostondf)
str(Bostondf$zn)
summary(Bostondf)

```

#Check the missing values no missing values--- Result: No missing values in the data
```{r}
sum(!complete.cases(Boston))

```

#check the co-relation matrix with target: lstat is highly co-related and Chas is leaast corelated

```{r}
sort(abs(cor(Bostondf$medv,Bostondf)))
cor(Bostondf)
```

#Build the linear model with all the 13 predictors : Adjusted R-squared:  0.7338  but predictors have Multicolinearity
```{r}
model=lm(medv~., data= Bostondf)
vif_data<- lm(medv~., data= Bostondf)
sort(vif(vif_data))
summary(model)
```
# Different model built looking at the P-Values and the correlation of independent variables with dependent variable
# Removed low corelated independent variables age and Indus
```{r}
model1 <-lm(formula = medv ~ chas + black + ptratio + rm + lstat, data = Bostondf)
sort(vif(model1))
summary(model1)
```

#Using PCA and building the model 
```{r}
library(caret)

trans = preProcess(Boston[,0:13],method = c("BoxCox","center","scale","pca"))
PC = predict(trans, Boston[,0:13])
X=trans$rotation
X
str(PC)
X1= PC
X1['medv']= Boston['medv']
```

```{r}
plot(PC)
```

```{r}
modelpca=lm(medv~PC1+PC2+PC3+PC4+PC5+PC7+PC8+PC9, data= X1)
vif_data<- lm(medv~PC1+PC2+PC3+PC4, data=X1)
sort(vif(vif_data))
summary(modelpca)
```
# With a R-Squared value of 0.753, it shows that the model is a good predictor 

# Remove heteroscedasticity
```{r}
bptest(modelpca)
vcovHC(modelpca, omega=NULL, type="HC4")
#Below is the most important code
coeftest(modelpca, df=Inf, vcov=vcovHC(model,type="HC4"))
```

